### 2015-07-05 narrative/intro.tex
cleanup the XGC1 use case

Take for example the latest use case for the XGC1 simulation from C. S. Chang (PPPL), who is one of the largest users of Leadership Class Facilities (over 300M hours at ALCF, NERSC, and OLCF). They launched a series of simulations, planning to produce 100~PB of data over 10 days of total runtime on the Titan system. An expert team was assembled from the user group, the middleware I/O team to help with the application I/O (using ADIOS), the local experts of the Lustre file-system and the tape archival system (HPSS). Due to physical resource limitations, the simulation was restricted to write about 10~PB initially, but then considering the time to write and read this much data on the tape archive system, and the financial costs to store it, this plan was cut again considerably. Note that such time and cost information was not known by the user; the HPSS expert had to inform everyone else about it. The user team had to make hard decisions of which data to save from the originally planned 100~PB. The file system experts told about the then-current file system limitations in size, performance and purge policy. The user then decided to write 0.5~PB per day (the individual daily simulation runs were and are going to be separated by many days or weeks), 5~PB in total, storing maximum of 2~PB of data on disks at a time and storing the rest on tape.

>>>>

Take for example the latest use case for the XGC1 simulation from C. S. Chang (PPPL), who is one of the largest users of Leadership Class Facilities (over 300M hours at ALCF, NERSC, and OLCF). They launched a series of simulations, planning to produce 100~PB of data over 10 days of total runtime on the Titan system. An expert team was assembled from the user group, the middleware I/O team to help with the application I/O (ADIOS), the local experts of the Lustre file-system and the tape archival system (HPSS). Due to physical resource limitations, the simulation was restricted to write about 10~PB initially. However, once the time to write and read, together with the financial cost to archive this much data were more fully explored, this plan was again signficantly reduced. At each stage, the particular expert knowledge regarding the lustre file system and the archival tape storage were not known to the user team. As these particulars were realized, significant modifications in the plans were made. Eventually, the user was forced to make very hard decisions in reducing the desired 100~PB over a 10-day run to a mere 5~PB of data. A maximum of 2~PB would be on disk, and the rest would be archived.
